Turbulence in compact to giant HII regions

### 2022-05-27 strucfunc_paper.tex
Javier changes 2022-05-20
Reorganise order of subsections in discussion
Javier changes 2022-05-27

We use \cite{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
These observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used with a étalon separation of 0.5 mm. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

@@

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).
%This \(L/2\) constrain is not used for the regions observed with MUSE.

@@

% Particularly the EON observations, which are the oldest, the fitting procedure gives a noise value of \SI{5.6}{km^{2}.s^{-2}} larger that the \(\sigma^2\pos\) value of \SI{3}{km^{2}.s^{-2}}.
% The derived correlation length \(r_0 = \SI{0.05}{pc}\) is \num{6} times smaller
% than the box size, which is the minimum value for this ratio of our sample. 
% Hence we can confirm that the finite map has no effect in our results.
% The derived seeing parameter \(s_0 = \SI{0.002}{pc}\), consistent with the Orion core fit, is more than \num{250} times smaller than \(r_0\).
% This large ratio is because the separation of the pixels for the EON observations are at separations above the observational seeing, so these parameter has virtually no effect in our model for the EON case.
% The previous statement can be confirmed with the Fig. \ref{fig:corner-Galactic}b which shows the corner plot for the EON.
% The RMS seeing posterior is flat, meaning that the values in that range doesn't modify the fit.

% This behavior is also seen in the Carina nebula and Lagoon nebula.
% The observations for this regions are from the FLAMES multi-fiber instrument (section \ref{sec:flames-multi-fiber} ) in which the fibers separation  (see Figure \ref{fig:velocity-maps}) is above the observational seeing for the regions.

@@

For the more distant sources, the principal observational limitation is the seeing.
In three of the four sources,
the derived values of \(s_0\) exceed 10\% of the correlation length.
This implies that the true power law slope \(m\) is less steep than
would be naively inferred from the observations
(compare the green and orange curves in Figure~\ref{fig:strucfunc-fit-ExtraGal}),
but at the same time the degeneracies between parameters
(Figure~\ref{fig:corner-ExtraGal})
lead to large uncertainties in the determination \(m\).
On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.
\subsection{On the reasonableness of the derived seeing widths and noise}
\label{sec:sanity-check-derived}
In the model fitting we allow the nuisance observational parameters
\(s_0\) and \(B\noise\) to vary freely within a wide range
(Table~\ref{tab:parameter-ranges}).
This is necessary because of the heterogeneous nature of our source datasets
and the fact that the details of the observational conditions
are not available to us in all cases.
However, it is worthwhile to perform a sanity check on the values that are implied by our model fits.
To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width for each fit in units of arcsec.
Disregarding the 3 sources where only upper limits can be determined,
the mean and standard deviation are \SI{0.95(30)}{arcsec},
which is perfectly consistent with expectations for seeing from ground-based observations.

@@

%structure functions plots descriptions
%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in solid and open blue circles the observational structure function that we compute using equation \ref{eq:Br} on the \ha{} velocity fields of Fig. \ref{fig:velocity-maps}. 
%In the plots the solid circles indicate the points we use in the non-linear regression analysis (see section~\ref{sec:model-fit}), while the open circles are the points of the structure function that where left out.
%The criteria for the previous considerations is that the structure function at large separations is affected by the inhomogeneties of the velocity field (see section-\ref{sec:limit-model-struct}).
%The points left our correspond to the largest separations that are not consider in our model. 
%In some cases, at the smallest separations we merge a couple of the structure functions points under the assumption that those would be heavily affected by the seeing.
%The Figures shows in the orange solid thick line the best fit for the equation \ref{eq:sf-functional} which takes into account observational limitations on the structure function.
%The green dashed line indicate the theoretical model for the structure function using equation \ref{eq:functional}.

%Figures \ref{fig:strucfunc-fit-OrionS}-\ref{fig:strucfunc-fit-OrionLH} left panels show in dashed and dotted lines the parameters of our model.
%The vertical dashed line indicates the correlation length, \(r_0\), and the horizontal dashed line indicates the true variance of the velocity fields, \(\sigma^2\).
%The vertical and horizontal dotted lines shows the value of the observational considerations: the rms seeing, \(s_0\) and the noise, \(B\noise\).
%These values were obtained using the LM method.
%For the dashed and dotted lines the overlapping translucent boxes indicate the confidence intervals in 1-sigma (dark shaded area) and 2-sigma (light shaded area) obtained from the MCMC analysis.
%The light shaded areas in the plot show where the separation \(r\) is above half of the box size, \(L\), which is indicated with a vertical dotted line.

@@

%corner plots descriptions
%Figures \ref{fig:corner-example-Orion} show the corner plots \citep{2017ascl.soft02002F} of the turbulent parameters and observational constraints
%(further examples in Appendix~\ref{sec:addit-covar-corn}).
%These plots shows the one and two dimensional projections of the posterior probability distributions of the parameters used in equation \ref{eq:chi}.
%They also show the distribution for each parameter independently in the histograms along the diagonal and then the marginalized two dimensional distributions in the other panels making possible to visualize all of the covariances between parameters \citep{2017ascl.soft02002F}.
%The contours in the plots reflect the 95\(\%\), 99\(\%\), 99.5\(\%\) and 99.9\(\%\) confidence intervals.
%A number of fits for the equations \ref{eq:sf-functional} and \ref{eq:functional} using samples of the posteriors are shown in thin translucent orange and green lines, respectively, showing the possible range of the confidence intervals.

%Table \ref{tab:Res} presents the turbulent parameters and observational constraints values mentioned in the paragraphs above.
%The confidence intervals for these values are up to 2-sigma of the posteriors.
%The second column correspond to the variance \(\sigma^2\pos\) of the velocity field.
%The \(B\noise\) value is shown in the third column which would be the minimum squared velocity difference that could be measure by the instrument.
%The fourth column in Table \ref{tab:Res} shows the rms seeing value in parsecs, \(s_0\), which represent the minimum value of the separation which would valid for the observed structure function. 
%The fifth column shows the correlation value \(r_0\) in parsecs.
%The \(r_0\) range covered in our results for the sample goes from 0.09 to 12 pc.
%The sixth column indicates the size of each observational box in parsecs.
%The index \(m\) is shown in the seventh column.
%The range covered by the power-law index goes from 0.7 to 1.5.
%The eighth column show the ratio \(L / r_0\)
%The last column shows the FWHM seeing in arcsec.
%The interpretation of our results is developed in the next section.

@@

In the next sections we discuss the application and interpretation of the turbulent parameters we obtained in our results.
%We present a resume of the turbulence theory and its validation to \hii{} regions.
%It is also mentioned some physical processes that contribute to stirring the ionized gas and the possibility that they are responsible for the observed velocity fluctuations.
We present the most important correlations between the turbulent parameters and physical properties of our \hii{} region sample and finally we discuss our results in the context of previous structure functions.

%\subsection{Turbulence}\label{sec:turbulence-theory}

%\textit{Will 2021-12-10: Moving this section to later for now. Maybe
%  this material could go in discussion.}

%The idea to treat the ionized regions from a fluid mechanic view is intuitive if we consider the continuum hypothesis. 
%We validate this hypothesis using the Knudsen number defined as \(\text{Kn} \equiv \lambda / l\), where \(\lambda\) is the mean free path of the medium and \(l\) a characteristic length of the phenomenon we are studying.
%Taking into account a \(\lambda_{\text{HII}}\) of \SI{2.7e-7}{pc} \citep{1941ApJ....93..369S} and a \(l_{\text{HII}}\) of \SI{1}{pc} for ionized regions we obtained \(\text{Kn} \approx 10^{-7}\), while in general the continuum approach is valid for \(\text{Kn}\ll 1\).

%A turbulent behavior in the flows is more common in fluid systems than a laminar one.
%These turbulent flows tends to be unsteady, irregular and chaotic, and the turbulent motions are observed in many scales. 
%The turbulent flows are associated with a high Reynolds numbers which is defined as \(\text{Re} = l v_{l} / \nu \), where \(v_{l}\) is a characteristic velocity in the fluid system and \(\nu\) is the kinematic viscosity of the medium.
%Experiments have shown that a flow which is laminar become turbulent when increasing the velocity (i.e., increasing the Re) and a large range of velocity fluctuation appear at all scales.
%A high Re reflects high ratio of the advection/difussion terms of the Navier-Stokes equations, being interpreted as that the inertial forces taking over the viscous ones. 
%Hence it is possible to assume that if viscosity is not dominant in a flow, this flow would be turbulent.

%As astronomical observation made it possible to measure a large number of points with a high accuracy, it was found that velocities show a non-thermal component reflecting characteristic of turbulent earthly flows.
%The existence of turbulent flows in astrophysical objects, ranging in scales from 10\(^6\) to 10\(^{17}\) m \citep{2010ApJ...710..853C} is thought to be consequence of the high \(Re\), between 10\(^4\) and 10\(^9\) \citep{1949ApJ...110..329C,lagrois2011} that characterized these objects.

%The classic turbulence theory assumes a three-dimensional isotropic, incompressible and subsonic flow that can be described using an energy spectrum formed by vortices or eddies of different sizes \citep{kolm1}.
%The concept of the energy spectrum assumes that the energy is cascading down inside the flow from the largest to the smallest scales.
%The different scales in the energy cascade are defined based on their Re.
%In one side of the spectrum there is the energy injection scale, \(L_I\), that is related to the largest vortices, called the integral scales, where \(\text{Re} \rightarrow \infty\).
%On the other side of the spectrum there is the dissipation of energy at small scales, \(l_I\), where  \(\text{Re} \rightarrow 1\) and it is assumed that small vortices are responsible for the friction that dissipates the energy flux into thermal energy.
%In between there is the inertial range, \(l_d  << l << L_I\), where in a stationary case the energy transfer is at a constant rate.

%The rate of transfer of specific energy \(\epsilon\) (energy per unit mass) in the inertial range is independent of the \(l\) scale having the form \(\epsilon \sim v_l^2 / \tau_l\), where the kinetic energy is of the order of \( v_l^2\) and the life time of a velocity fluctuation is \(\tau_l\), which can be can be put in terms of \(\tau_l \sim l / v_l\). 
%Hence we obtain \( v_l \sim (\epsilon l)^{1/3}\) where \(\epsilon\) is invariant in the cascade.

%The energy cascade is described using the energy spectrum, $E(k) \propto k^{\beta}$ where \(k\) is the wave number for a determined scale \(l\) ($k \equiv l^{-1}$).
%The total specific energy of a determined $l$ scale is of the order \(\langle v_{l}^{2} \rangle \) and is the energy integral above the associated \(k\), defined as:

%\begin{equation}\label{eq:energy-spectrum}
% \langle v_{l}^{2} \rangle = \int_{k}^{\infty} E(k)dk
%\end{equation}
%
%If it is assumed that this energy is of the order of $(\epsilon l)^{\frac{2}{3}} \sim (\frac{\epsilon}{k})^{\frac{2}{3}}$ we can differentiate equation \ref{eq:energy-spectrum} and obtained the final form:

%\begin{equation}\label{eq:kolmogorov-law}
%E(k) \propto \epsilon^\frac{2}{3} k^{-\frac{5}{3}}
%\end{equation}
%
%where \(\beta = -5 / 3\) is the Kolmogorov law.
%For supersonic turbulence the index is $\beta=-2$ \citep{burg}.

%Using a statistical law that relates the moments \(M_n\) of order \(n\) with the increments in the velocity field for a separation \(\boldsymbol{r}\) \citep{Leqism}, we have:

%\begin{equation}\label{eq:velocity-moments}
%M_n = \langle \vert \boldsymbol{v}(\boldsymbol{x} + \boldsymbol{r})- \boldsymbol{v}(\boldsymbol{x})\vert^n \rangle \propto (\epsilon r)^{n/3}
%\end{equation}
%
%the average is over all the positions \(\boldsymbol{x}\) and directions \(\boldsymbol{r}\). 
%The Kolmogorov model predicts that the moment of order 2, the second-order structure function (equation \ref{eq:Br}), follows \(M_2 \propto r^{2/3}\).

%\subsection{Origins of interstellar turbulence}\label{sec:origins-turbulence}

%In the particular case of GEHR, as supersonic motions dissipate energy by shocks in time scales relatively short compared with the age of the region, it is necessary an energy source to replenish continuously the energy lost. From the observed velocity  dispersion \(\sigma\), and assuming that we have an isotropic distribution of velocities,  we can estimate the 3D velocity dispersion by \(\sigma_\mathrm{3D} = \sqrt{3} \sigma\). The mass of the ionized gas together with the velocity dispersion \(\sigma_\mathrm{3D}\)  are used to estimate the kinetic energy in the GEHRs.
%As these objects have typically  masses of the ionized gas of \num{\sim e5} M\(_{\sun}\) and velocity dispersion values  of \SI{\sim 20}{km.s^{-1}} \citep{1984ApJ...287..116K}, typical kinetic energy of the ionized gas is \SI{\sim e51}{ergs}.

%In the standard Kolmogorov model, the energy spectrum of turbulence becomes dependent only on \(\epsilon\), the mean dissipation of energy per unit time per unit mass of fluid,  with the inertial forces transferring without losses kinetic energy from larger to smaller turbulent elements within the inertial range. Let \(L_c\) be the characteristic length of the largest eddies, and \(\delta v\) the typical velocity.

%We have then that \(\epsilon = (\delta v)^{3}/L\). In steady-state turbulence, equilibrium exists between the energy input and the energy dissipation rates. 
%Although the present observations indicate that turbulence in \hii{} regions may not follow the Kolmogorov model, with energy input occurring at different scales, so that a  truly inertial range may not exist at all, lets us make a crude estimation of the  amount of energy transferred between scales using this simple model. 
%Assuming the above figures for the mass of the gas and velocity dispersion, \(\delta v = \sigma_\mathrm{3D}\),  and a \(L_c\) of \SI{100}{pc}, we obtain that the energy transfer rate \SI{\sim e37}{erg.s^{-1}}, and  the time scale for energy transfer, \(L/\delta v \), would be of few million years.

%There are several energy sources that could provide or contribute  to the energy required: of the order of kpc, the differential rotations of the galaxy that produces shear at large scale, at scales of the order of hundreds of pc, supernova explosions inject a large amount of kinetic energy.
%At scales of several tens of pc the expansion of \hii{} regions and stellar winds are a source of energy and, bipolar flows, shocks, jets and champagne flows inject energy at small scales about one tenth of a pc.

%The lack of precise information on how these mechanism contribute to the emission line broadening make a non-trivial task to determine at what extent they play a role in the interstellar turbulence, contributing to the complexity of the extraction of pure turbulent motions from velocity profiles in nebulae \citep{2011MNRAS.413..705L,arthur2016turbulence}.

@@

\subsubsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two. The size of the markers represent the distance to each region.}
\label{fig:los-vs-pos}
\end{figure}

%Intro for scaling relations
Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion have been used as tools for finding scaling relationships for these objects.
These kind of relations have also been found in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}
In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for \halpha\ size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. }
\label{fig:sigvsl}
\end{figure}

In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
Since this is the first time a model of this type is applied to a sample of HII regions (at least for our knowledge), our results are bounded to be different from previous investigations, including the one that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.

A complete analysis on different emissions lines of the structure function on Orion was carried out by \citet{arthur2016turbulence}. 
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
This results just consider one component on the Gaussian fit. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \(\approx\) 0.05 pc. For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}.

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Doradus complex, finding no indication of turbulent motions between scale of 10 and 100 pc.
These result is consistent with Fig. \ref{fig:strucfunc-fit-MC}a showing that the turbulent motions are correlated at scales \(<\) \SI{5}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from 3 to 200 pc.
In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula as their observations cover a region where the large-scale velocity fluctuations are uncorrelated as in the case of \citet{1961MNRAS.122....1F}.
From the observations where are using this is the first time turbulence characterized in 30 Doradus using the structure function.

For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
Despite this general agreement the interpretations in each study is different.
\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
None of the previous studies present a power-law index for the structure function to compare our results.

\subsection{Final remarks}

The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles. 
The asymmetry in the emission line indicates coherent mass flow motions, 
and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
a mixture of coherent and chaotic flows. 
Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%a single inertial scale where the ionized gas behavior can be described by means of a power law.

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of 49.9 kpc \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for 40 pc and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

For a correct analysis on the structure function it is necessary to consider the consequences that the observational box size and the seeing have on the results.
To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma^2 \).

>>>>

We use \citet{1987A&A...176..347H} observations to analyze the Extended Orion Nebula.
These observations were obtained using a 106 cm-Cassegrain telescope at Observatorium Hoher List. 
A Fabry-Pérot interferometer was used with a étalon separation of 0.5 mm. 
A number of fifteen interferograms have been taken with different pointing directions of the telescope's optical axis in the nebula with an exposure time between 10 and 40 minutes. 
The exposures are overlapped and fall into one square of a grid with a width of 1' centered at \(\theta^{1}\)Ori C.

@@

For the observational values (\(B\obs(r)\); blue symbols),
the structure function is the average value of equation~\eqref{eq:Br}
over all pairs of points that contribute to each radial bin.
The uncertainty of each bin (blue error bars) is estimated
as the standard deviation of these values divided by the square root of
the number of contributing pairs.
\textit{But this is not true -- we use constant fractional error with adjustments for small and large separations.}
For most sources a fixed bin size of \SI{0.05}{dex} is used,
but for those observed with multi-fiber spectroscopy
(Carina and M8, see section~\ref{sec:flames-multi-fiber}),
where coverage is sparse at small separations,
adjacent bins were merged to ensure at least 100 pairs contribute to each bin.
Bins with separation less than \(L/2\) are used to constrain the model fitting (filled symbols),
while larger separations (open symbols) are not used
since they are more likely to be affected by a breakdown
of the homogeneity assumption (see section~\ref{sec:limit-model-struct}).

@@

@@

For the more distant sources, the principal observational limitation is the seeing.
In three of the four sources,
the derived values of \(s_0\) exceed 10\% of the correlation length.
This implies that the true power law slope \(m\) is less steep than
would be naively inferred from the observations
(compare the green and orange curves in Figure~\ref{fig:strucfunc-fit-ExtraGal}),
but at the same time the degeneracies between parameters
(Figure~\ref{fig:corner-ExtraGal})
lead to large uncertainties in the determination \(m\).
On the other hand, the values of \(r_0\) and \(\sigma^2\) are still well-constrained.

\subsection{On the reasonableness of the derived seeing widths and noise}
\label{sec:sanity-check-derived}
In the model fitting we allow the nuisance observational parameters
\(s_0\) and \(B\noise\) to vary freely within a wide range
(Table~\ref{tab:parameter-ranges}).
This is necessary because of the heterogeneous nature of our source datasets
and the fact that the details of the observational conditions
are not available to us in all cases.
However, it is worthwhile to perform a sanity check on the values that are implied by our model fits.
To that end, the last column in Table~\ref{tab:Res} lists the FWHM seeing width for each fit in units of arcsec.
Disregarding the 3 sources where only upper limits can be determined,
the mean and standard deviation are \SI{0.95(30)}{arcsec},
which is perfectly consistent with expectations for seeing from ground-based observations.

@@

@@

@@

In the following sections, the results shown previously are discussed and compared with the structure functions of previous investigations that analyzed \hii{} regions from our sample.
We present the most important correlations between the turbulent parameters and the physical properties from the \hii{} region sample and finally an interpretation of the turbulent parameters is given.

In Section \ref{sec:methods-apply} we mentioned the model we propose for the structure function.
Since this is the first time a model of this type is applied to a sample of HII regions, our results are bounded to be different from previous investigations, including the investigations that have the same observations as \citet{arthur2016turbulence} and \citet{Medina-Tanco:1997a,Melnick:2021x}.

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30~Doradus complex, finding no indication of turbulent motions between scale of \num{10} and \SI{100}{pc}.
\citet{Melnick:2021x} also investigated the structure function in 30 Doradus finding on their results that the structure function is entirely flat on scales from \num{3} to \SI{200}{pc}.
The above does not coincide with our results, since we establish the existence of correlations up to the maximum value of the structure function that occurs at \SI{20}{pc}, separation where a value of 2\(\sigma\pos^2\) is reached.
The VLT FLAMES/GIRAFFE observations of \citet{Melnick:2021x} may not have had the resolution to resolve the correlations at small separations, however an inspection of its velocity map (figure 7 in their work) shows that the velocity distribution it is far from completely random.
This is the first time turbulence is characterized in 30~Doradus using the structure function.

For NGC 604 there is good agreement in our structure function results and previous studies because where are using the same TAURUS-II data as \citet{Melnick:2021x} and \citet{Medina-Tanco:1997a}.
Despite this general agreement the interpretations in each study is different.
\citet{Medina-Tanco:1997a} conclude about a double regime acting on the kinetic energy spectrum.
According to this double cascade, turbulence is being forced at scales of \(\approx\) \SI{10}{pc} while and energy cascade has developed down to the smallest scales and other, as an inverse cascade, extends up to scale of \(\approx\) \SI{70}{pc}.
\citet{Medina-Tanco:1997a} mentioned different characteristic scale lengths, the most notorious is the \SI{\sim 10}{pc}, and they interpret it as possible source on energy associated with the expansion of shocks coming from wind bubbles.  
\citet{Melnick:2021x} addresses some issues with TAURUS II data while comparing profiles between the previous instrument TAURUS I where there exist a difference between observations (see section 4.1 on their paper).
They mentioned that one problem with \citet{Medina-Tanco:1997a} structure function is that they didn't take into account the observational seeing.
This would invalidate they results and \citet{Melnick:2021x} consider that taking out the structure function values that fall within this range would make the structure function flat at scales \(<\)\SI{10}{pc}, so they rule out \citet{Medina-Tanco:1997a} results.
Finally they point out, and we agree, the importance of observing NGC 604 at higher spatial resolution. 
Our Fig. \ref{fig:strucfunc-fit-ExtraGal}d shows in fact that there is a velocity structure in NGC 604. 
None of the previous studies obtained a power-law index or correlation length for the structure function to compare our results.

%Intro for scaling relations
Correlations between the physical properties of \hii{} regions like size, luminosity, and the velocity dispersion have been used as tools for finding scaling relationships for these objects.
These kind of relations have also been found in dwarf galaxies and high-redshift star formation regions.
\citet{melnick1977,terlevich1981} were the first to shown an empirical relationship between the line width and the integrated properties of the \hii{} regions as the diameter or the luminosity (\(r \sim \sigma ^{\sim 2}\) ; \(\text{L}_{\text{H}} \sim \sigma ^{\sim 4}\)).
In later years, \citet{1988A&A...201..199A} confirmed these relationships considering the discrepancies of previous investigations obtaining \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.9}\) and \(r \propto \sigma^{1.84}\).
%\citet{1981MNRAS.194..809L}
In recent years, \citet{2012MNRAS.422.3339W} have found that clumps and \hii{} regions follow scaling relations over the range of z = 0-2 for the \halpha\ emission line with the size, velocity dispersion, luminosity and mass, finding \(\sigma \propto r^{0.42}\), \(\text{L}_{\text{H}_{\alpha}} \propto r^{2.72}\) and \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{4.18}\), respectively. 
This results imply that the same process are seen at high redshifts and the current epoch in star forming regions.
Recently, \citet{Moiseev:2015a} found that the relation in dwarf galaxies is \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{5}\).
\citet{2018MNRAS.474.1250F} presented the relationship between integrated H$_{\beta}$ line luminosity and the velocity dispersion for new data of 36 giant HII regions obtaining \(\text{L}_{\text{H}_{\beta}} \propto \sigma^{5.02 \pm 0.21}\).

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions. }
\label{fig:sigvsl}
\end{figure}

\subsection{Relationship between plane-of-sky and line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{The \(\sigma_{\text{pos}}\)-\(\sigma_{\text{los}}\) plane. The dotted line represents slope equal to unity and the dashed line represents a slope of two.}
\label{fig:los-vs-pos}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The observations point out to the existence of spatial correlation between velocities, that could be interpreted as turbulence. 
Arguments against the existence of true, isotropic turbulence can be raised as, for example: i) the histograms of velocity are not always Gaussian, ii) only a fraction of the integrated emission lines of the \hii{} regions show true Gaussian profiles. 
The asymmetry in the emission line indicates coherent mass flow motions, 
and sometimes is considered incompatible with turbulence. However, turbulence is in fact 
a mixture of coherent and chaotic flows. 
Only at the regime of the so-called fully developed turbulence the non-linear phenomena dominate completely the movement and the chaotic flow prevail. 
The problem here is that a straightforward test for any turbulent model is a big challenge, as we are in the presence of many entangled effects. 
However, the circumstantial evidence in favor of the existence of turbulent motions in \hii{} regions is overwhelming, and many are the potential sources of energy to create and maintain turbulence during the lifetime of an \hii{} region.

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

For a correct analysis on the structure function it is necessary to consider the consequences that the observational box size and the seeing have on the results.
To quantify the impact of these considerations on the final structure function, we perform a series of experiments using artificial turbulent velocity maps.
In particular, our interest is to quantify how this observational limitations affect the determination of parameters such as the correlation length, \(r_0\), and the velocity field variance, \(\sigma\pos^2 \).
